---
title: "Currency Report"
output: 
  prettydoc::html_pretty:
    theme: cayman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(purrr)
library(stringr)
library(DT)
library(quantmod)
library(magrittr) 
library(dplyr)
library(lubridate)
library(prettydoc)

currencies <- read.csv("currency_tables.csv")

currency.list <- currencies$Symbol %>% unique() %>% paste0()
currency.data <- map(currency.list, function(i) getSymbols(i, src = "FRED", getsymbols.warning4.0 = FALSE, auto.assign = FALSE))

```

# Quarterly Returns

```{r quarterly report, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
q.returns <- map(currency.data, quarterlyReturn)
q.returns <- reduce(q.returns, merge.xts)
q.report <- q.returns %>% 
  setNames(c("EURO", 
              currencies %>% 
                filter(Symbol != "DEXUSEU") %>% 
                pull(Name) %>% as.character)) %>% 
  tail(10)

q.rnms <- paste0(q.report %>% index() %>% year, " Q", q.report %>% index() %>% quarter)

datatable(q.report, rownames = q.rnms, 
          options = list(searching = FALSE, 
                         paging = FALSE,
                         info = FALSE,
                         scrollX = TRUE)
          ) %>% 
  formatPercentage(columns = c(1:ncol(q.report)))
```
*EURO Countries: Austria, Belgium, Cyprus, Estonia, Finland, France, Germany, Greece, Ireland, Italy, Latvia, Lithuania, Luxembourg, Malta, Netherlands, Portugal, Slovakia, Slovenia, Spain*

----
<!--BR--><!--BR--><!--BR-->

# Annual Returns

```{r annual report, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
a.returns <- map(currency.data, annualReturn)
a.returns <- reduce(a.returns, merge.xts)
a.report <- a.returns %>% 
  setNames(c("EURO", 
              currencies %>% 
                filter(Symbol != "DEXUSEU") %>% 
                pull(Name) %>% as.character)) %>% 
  tail(10)

a.rnms <- paste0(a.report %>% index() %>% year)

datatable(a.report, rownames = a.rnms, 
          options = list(searching = FALSE, 
                         paging = FALSE,
                         info = FALSE,
                         scrollX = TRUE)
          ) %>% 
  formatPercentage(columns = c(1:ncol(a.report)))
```
*EURO Countries: Austria, Belgium, Cyprus, Estonia, Finland, France, Germany, Greece, Ireland, Italy, Latvia, Lithuania, Luxembourg, Malta, Netherlands, Portugal, Slovakia, Slovenia, Spain*
